Accuracy in Parameter Estimation and Simulation Approaches for Sample Size Planning Accounting for Item Effects

### 2024-11-11 manuscript_draft.Rmd
updating the manuscript submission

```{r bimodal-results, fig.cap = "Estimated sample sizes for distributions that vary in the number of bimodal items. Note that percent below is treated as a continuous factor", fig.height=8, fig.width=8}
ggplot(bi_DF, aes(x = percent_below,
                  y = corrected_sample_size, 
                  color = factor(size),
                  shape = factor(size))) +
  geom_point(size = 3) +
  geom_line() +
  theme_classic() +
  xlab("Percent of Items Below Threshold") + 
  ylab("Corrected Sample Size") +
  scale_color_viridis_d(option = "plasma") +  # Use the 'plasma' viridis option
  scale_shape_manual(values = c(16, 17, 18, 19, 15, 3, 7, 8, 9, 13, 10)) +
  labs(color = "Size", shape = "Size")
```

>>>>

```{r bimodal-results, fig.cap = "Estimated sample sizes for distributions that vary in the number of bimodal items. Note that percent below is treated as a continuous factor, and therefore, some estimates are the same (i.e., below 80 and 85 percent may be both estimated as 88%).", fig.height=8, fig.width=8}
ggplot(bi_DF, aes(x = percent_below,
                  y = corrected_sample_size, 
                  color = factor(size),
                  shape = factor(size))) +
  geom_point(size = 3) +
  geom_line() +
  theme_classic() +
  xlab("Percent of Items Below Threshold") + 
  ylab("Corrected Sample Size") +
  scale_color_viridis_d(option = "plasma") +  # Use the 'plasma' viridis option
  scale_shape_manual(values = c(16, 17, 18, 19, 15, 3, 7, 8, 9, 13, 10)) +
  labs(color = "Size", shape = "Size")
```
